### 2023-12-12 main.tex
ss

For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is given by 

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation \eqref{exactCorrelations}.}
\todo{Explain this expectation...}

>>>>

For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is fully determined by the correlations of equation \eqref{exactCorrelations} through the relation 

@@

% {\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation
% \eqref{exactCorrelations}.}
\todo{Are you ok with that? It is still not super clear....}
